Refinements for open automata

### 2022-05-13 2021-Refinement/paper/refinementarticle.tex
definition to discuss
meeting note

@@

\TODO{
A string $t \in \mathcal{A}^*$ is a trace of an automaton if there is some state $s$ such that $s_0 \xrightarrowdbl{t}  s$. We denote the set of traces of an automaton $A$ by $\mathcal{T}_A$. \\
Notion of Extension refinement. May be we need to introduce the notion of  refusal of
a trace $t \in \mathcal{T}_A$ is a set of actions such that all actions in the set can be refused after the automaton $A$
has executed the trace $t$. \[X \in \bot_{A}(t) \Leftrightarrow \{\exists s. s_0  \xrightarrowdbl{t} s \wedge \forall a \in X. s \not{\xrightarrow{a}}    \}\] and replace deadlock reducing, under (3) by
\[\forall t \in \mathcal{T}_{A_1} \cap  \mathcal{T}_{A_2},\, \bot_{A_2}(t) \subseteq  \bot_{A_1}(t)  \] } 
\begin{lemma}[Tracked holes] By construction, if an automaton is the refinement of another one, it is also a refinement by tracking less holes.
\[\wrel{A_1}{A_2}{H} \land H'\subseteq H \implies \wrel{A_1}{A_2}{H'}\]
\end{lemma}
\TODO{example}

>>>>

\begin{definition}[XXX]\label{def:???} \TODO{To check}\\
Let \(\OAg[1]\) and \(\OAg[2]\) be two OAs.
A relation \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) on OA   is XXXX if  it satisfies the following:
\begin{multline*}
\forall \mpar{s_1, s_2} \in S_1 \times S_2,  V_1 \uplus V_2\vdash \\ \bigsymb{\exists} \mpar{t_1, t_2} \defobject \mpar{\OTx{1}{}{1}{1}, \OTx{2}{}{2}{2}} \in \fOT{s_1} \times \fOT{s_2} \wedge R\mpar{s_1, s_2} \wedge 	g_1 \wedge g_2 \wedge \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j}\\ \implies  R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2}\\
\end{multline*}
\end{definition}

@@

\TODO{
A string $t \in \mathcal{A}^*$ is a trace of an automaton if there is some state $s$ such that $s_0 \xrightarrowdbl{t}  s$. We denote the set of traces of an automaton $A$ by $\mathcal{T}_A$. \\
Notion of Extension refinement. May be we need to introduce the notion of  refusal of
a trace $t \in \mathcal{T}_A$ is a set of actions such that all actions in the set can be refused after the automaton $A$
has executed the trace $t$. \[X \in \bot_{A}(t) \Leftrightarrow \{\exists s. s_0  \xrightarrowdbl{t} s \wedge \forall a \in X. s \not{\xrightarrow{a}}    \}\] and replace deadlock reducing, under (3) by
\[\forall t \in \mathcal{T}_{A_1} \cap  \mathcal{T}_{A_2},\, \bot_{A_2}(t) \subseteq  \bot_{A_1}(t)  \] }

\TODO{thm: our new definition is equivalent to extension refinement in case there is no hole and no guard}

\begin{lemma}[Tracked holes] By construction, if an automaton is the refinement of another one, it is also a refinement by tracking less holes.
\[\wrel{A_1}{A_2}{H} \land H'\subseteq H \implies \wrel{A_1}{A_2}{H'}\]
\end{lemma}
\TODO{example}
